---
title: "Examining Dangerous Spots for Pedestrians near Schools"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    source_code: embed
    vertical_layout: scroll
    orientation: rows
runtime: shiny
---

```{r, setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(ggplot2)
library(DT)
library(stringr)
library(dplyr)
library(tools)
library(plotly)
library(rsconnect)
library(rgdal)
library(leaflet)
library(leaflet.extras)
library(sp)
library(rgdal)
library(rgeos)
library(htmltools)
library(RColorBrewer)

# Load crash location file
crash <- read.csv(file = "AC_Major_Crashes_Filtered.csv")

# Load school location file
schools <- read.csv(file = "pps_schoolsapr2019publish.csv")

# Subset school file
schools_subset <- subset (schools, select = c(name, latitude, longitude))

```
Inputs {.sidebar}
-----------------------------------------------------------------------
```{r, sidebar}
# User selects which year to graph-------------------------------------------
sliderInput("year", "Year(s)",
            min = (2010), max = (2019),
            value = c(2019), sep = ""
            )

# Download data button
downloadButton("downloadData", "Download")

```
Outputs

Row {data-height=150}
-----------------------------------------------------------------------
### Introduction

This dashboard displays crashes in Allegheny County in the 10-year period 2010-2019 that resulted in a pedestrian's death or major injury. Schools are shown to highlight those spots where children are likely to be walking.


Row {data-height=650, .tabset}
-----------------------------------------------------------------------
### Subset Crash Data

```{r, map }
# Subset crash data based on year input
crash_subset <- reactive({
  crash %>%
    filter(
      CRASH_YEAR %in% input$year, 
      PED_DEATH_COUNT == 1 | PED_MAJ_INJ_COUNT == 1
    )
})

# Create icon for schools
schoolIcon <- makeIcon(
  iconUrl = "https://i.pinimg.com/originals/b1/b7/de/b1b7de37299d6d589ba3d7e28652869b.png",
  iconWidth = 25, iconHeight = 25,
  iconAnchorX = 22, iconAnchorY = 94)

# Create blank basemap
map <- renderLeaflet({
  leaflet() %>%
    addProviderTiles("OpenStreetMap.Mapnik", options = leafletOptions(minZoom = 5, maxZoom = 18)) 
  })

# Set color palette based on death
observe({
  factor_ped_death_count <- factor(crash_subset()$PED_DEATH_COUNT) 
  binpal <- colorBin("Blues", factor_ped_death_count, 2, pretty = FALSE)
  
# Add crash and school layers to map
leafletProxy("map") %>% 
  addCircles(data = crash_subset(), lat = crash_subset()$DEC_LAT, lng = crash_subset()$DEC_LONG, color =
               ~binpal(factor_ped_death_count), group = "Crashes", popup = paste("Year: ",
                                                                                 crash_subset()$CRASH_YEAR, "<br>",
                                                                                 "Ped Death Count: ",
                                                                                 crash_subset()$PED_DEATH_COUNT,
                                                                                 "<br>", "Ped Major Injury Count: ",
                                                                                 crash_subset()$PED_MAJ_INJ_COUNT)) %>%
  addMarkers(data = schools_subset, icon = schoolIcon, group = "Schools", popup = schools_subset$name) %>%
  addLayersControl( # Add group controls
   overlayGroups = c("Crashes","Schools"),
    options = layersControlOptions(collapsed = FALSE)) %>%
  addLegend(position = "topleft", pal = palcrashes, values = crash_subset()$PED_DEATH_COUNT, # Add legend
            title = "Consequence of Crash",
            opacity = 1)
})
```

### Chart 1: Collision Causes

```{r, collision causes plot}

# Find counts of collision causes
observe({
alcohol <- sum(crash_subset()$ALCOHOL_RELATED)
cellphone <- sum(crash_subset()$CELL_PHONE)
speeding <- sum(crash_subset()$SPEEDING_RELATED)
fatigue <- sum(crash_subset()$FATIGUE_ASLEEP)
drugs <- sum(crash_subset()$DRUG_RELATED)

reason <- c("Alcohol","Cellphone","Speeding", "Fatigue", "Drugs")
count <- c(alcohol, cellphone, speeding, fatigue, drugs) 

# Create data frame of collision causes
causedf <- data.frame(reason, count)
})

# Create lollipop graph of collision causes
renderPlotly({
    (ggplotly(ggplot(causedf, aes(x = reason, y = count)) +
               geom_point(size = 3)+
                geom_segment(aes = reason,
                             xend = reason,
                             y = 0,
                             yend = unt)) +
               labs(title = "Common Causes of Crashes Involving Pedestrians",
                    subtitle = "from subsetted data")
    )})
```

### Chart 2: Hours of Crashes

```{r, hours of crashes plot}

# Create tibble of tallies of crashes per hour in the day
observe({
  hour_tallies <- crash_subset %>% count(HOUR_OF_DAY, name = "n_hour_of_day") })

# Create barchart from tibble
renderPlotly({
    (ggplot(hour_tallies, aes(x = HOUR_OF_DAY, y = n_hour_of_day)) +
            geom_bar(fill = "blue") +
            labs(y = "Count",
                 x =  "Hour of Day",
                 title = "The Distribution of Job Reallocation Rates across the States, 2004-2018"
                )
    )})

```

### Data Table

```{r, data table}
# Create data table corresponding to selected data
table <- renderDataTable(crash_subset(), options = list(pageLength = 10, autoWidth = TRUE, columnDefs = list(list(width = "8px", targets = "all"()))), 
                    rownames = FALSE)

table
```

### Download Handler

```{r, downloadhandler}
downloadHandler(
  filename = function() {
    paste("crashdata-", Sys.Date(),".csv",sep="")
  }
  content = function(file {
    write.csv(crash_subset(),file)
  })